Prediction of 2024 US election ...

### 2024-11-04 paper/paper.qmd
update paper
colin code update8

## Basic Model
```{r}
#| label: fig-model-pct-pollscore
#| echo: false
#| warning: false
just_harris_data = Harris_data |> na.omit()
lm_model1 = lm(pct ~ pollscore, data = just_harris_data)
predictions = predict(lm_model1, just_harris_data)
# summary(lm_model1)

@@

>>>>

## Basic  SLR Model
```{r}
#| label: fig-model-pct-pollscore
#| echo: false
#| warning: false
just_harris_data = Harris_data |> na.omit()
lm_model1 = lm(pct ~ pollscore, data = just_harris_data)
predictions = predict(lm_model1, just_harris_data)
# summary(lm_model1)

@@

```{r}
#| label: fig-model-pct-sample_size
#| echo: false
#| warning: false
lm_model1 = lm(pct ~ sample_size, data = just_harris_data)
predictions = predict(lm_model1, just_harris_data)
# summary(lm_model1)

ggplot(just_harris_data, aes(x = pct, y = predictions)) +
  geom_point(color = 'blue') +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red") +
  labs(title = "Actual vs Predicted Values",
       x = "Actual pct",
       y = "Predicted pct") +
  theme_minimal()

@fig-model-pct-sample_size The distribution of the points suggests that the model might not capture much variability in pct when sample_size is the only predictor. This indicate that sample_size has limited impact on pct.

```{r}
# lm_model1 = lm(pct ~ sample_size + pollscore, data = just_harris_data)
# predictions = predict(lm_model1, just_harris_data)
# # summary(lm_model1)

# ggplot(just_harris_data, aes(x = pct, y = predictions)) +
#   geom_point(color = 'blue') +
#   geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red") +
#   labs(title = "Actual vs Predicted Values",
#        x = "Actual pct",
#        y = "Predicted pct") +
#   theme_minimal()
```

## MLR Model
